CdGF_aucrf

### 2017-01-11 code/CdGF_AUCRF.Rmd
add cal plot for each model

LOsO_probs <- c()
LOsO_rf <- c()
for(i in 1:length(source_list)){
  source <- LOsO_df$human_source == source_list[i]
  LOsO_predict <- select(LOsO_df, -human_source)
  train <- LOsO_predict[!source,]
  test <- LOsO_predict[source,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOsO_rf[[i]] <- temp_model$RFopt
  LOsO_probs[LOsO_df$human_source == source_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOsO_roc <- roc(LOsO_df$Euth_Early~LOsO_probs)

#### leave-2-out
LTsO_df <- Predict_df %>% 
                select(Euth_Early, human_source, one_of(om_import_otus))
donor_list <- as.character(unique(LTsO_df$human_source))

LTsO_probs <- c()
LTsO_rf <- c()
for(i in seq(1,length(donor_list),2)){
  set.seed(seed)
  donors <- sample(donor_list)
  by_donor <- LTsO_df$human_source %in% donors[i:(i+1)]
  LTsO_predict <- select(LTsO_df, -human_source)
  train <- LTsO_predict[!by_donor,]
  test <- LTsO_predict[by_donor,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LTsO_rf[[i]] <- temp_model$RFopt
  LTsO_probs[LTsO_df$human_source %in% donors[i:(i+1)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LTsO_roc <- roc(LTsO_df$Euth_Early~LTsO_probs)

@@

om_loo_aucs <- c() 
om_loo_all <- c() 
for(j in 1:iters){ 
  set.seed(j) 
  mouse_set <- om_loo_df %>%  
    group_by(human_source) %>%  
    sample_n(1) %>% ungroup()  
  om_loo_probs <- c() 
  om_source_import <- data.frame(otu = om_import_otus) 
  for(n in unique(as.character(mouse_set$human_source))){ 
    train <- mouse_set[mouse_set$human_source != n, ] 
    test <- om_loo_df %>%  
      filter(human_source %in% n) 
    set.seed(seed) 
    temp_model <- AUCRF(Euth_Early~., data=select(train, -mouse_id, -human_source), 
                        pdel=0.99, ntree=500, ranking = 'MDA') 
    om_loo_probs <- rbind(om_loo_probs, 
                          data.frame(obs = test$Euth_Early, 
                                     pred = predict(temp_model$RFopt, 
                                                    test, type='prob')[,2])) 
    om_source_import <- merge(om_source_import,
                            data.frame(otu = names(temp_model$ranking), 
                                       rank = rank(temp_model$ranking)/
                                              max(rank(temp_model$ranking))),
                            by = 'otu', all.x = T, 
                            suffixes = c('',paste0('_', n)))
  } 
  om_loo_roc <- roc(om_loo_probs$obs~om_loo_probs$pred) 
  om_loo_otus <- merge(om_loo_otus, om_source_import,
                       by = 'otu', all.x = T, suffixes = c('',paste0('_',j)))
  om_loo_all <- rbind(om_loo_all, om_loo_probs) 
  om_loo_aucs[j] <- om_loo_roc$auc 
} 
om_loo_roc <- roc(om_loo_all$obs~om_loo_all$pred)

>>>>

LOsO_probs <- c()
LOsO_rf <- c()
for(i in 1:length(source_list)){
  source <- LOsO_df$human_source == source_list[i]
  LOsO_predict <- select(LOsO_df, -human_source)
  train <- LOsO_predict[!source,]
  test <- LOsO_predict[source,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LOsO_rf[[i]] <- temp_model$RFopt
  LOsO_probs[LOsO_df$human_source == source_list[i]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LOsO_roc <- roc(LOsO_df$Euth_Early~LOsO_probs)
LOsO_cal <- calibration_plots(data.frame(obs=LOsO_df$Euth_Early,
                                         pred=LOsO_probs))
#### leave-2-out
LTsO_df <- Predict_df %>% 
                select(Euth_Early, human_source, one_of(om_import_otus))
donor_list <- as.character(unique(LTsO_df$human_source))

LTsO_probs <- c()
LTsO_rf <- c()
for(i in seq(1,length(donor_list),2)){
  set.seed(seed)
  donors <- sample(donor_list)
  by_donor <- LTsO_df$human_source %in% donors[i:(i+1)]
  LTsO_predict <- select(LTsO_df, -human_source)
  train <- LTsO_predict[!by_donor,]
  test <- LTsO_predict[by_donor,]
  set.seed(seed)
  temp_model <- AUCRF(Euth_Early~., data=train, pdel=0.99, ntree=500)
  LTsO_rf[[i]] <- temp_model$RFopt
  LTsO_probs[LTsO_df$human_source %in% donors[i:(i+1)]] <- predict(temp_model$RFopt, test, type='prob')[,2]
}
LTsO_roc <- roc(LTsO_df$Euth_Early~LTsO_probs)
LTsO_cal <- calibration_plots(data.frame(obs=LTsO_df$Euth_Early,
                                         pred=LTsO_probs))

@@

om_loo_aucs <- c() 
om_loo_all <- c() 
for(j in 1:iters){ 
  set.seed(j) 
  mouse_set <- om_loo_df %>%  
    group_by(human_source) %>%  
    sample_n(1) %>% ungroup()  
  om_loo_probs <- c() 
  om_source_import <- data.frame(otu = om_import_otus) 
  for(n in unique(as.character(mouse_set$human_source))){ 
    train <- mouse_set[mouse_set$human_source != n, ] 
    test <- om_loo_df %>%  
      filter(human_source %in% n) 
    set.seed(seed) 
    temp_model <- AUCRF(Euth_Early~., data=select(train, -mouse_id, -human_source), 
                        pdel=0.99, ntree=500, ranking = 'MDA') 
    om_loo_probs <- rbind(om_loo_probs, 
                          data.frame(obs = test$Euth_Early, 
                                     pred = predict(temp_model$RFopt, 
                                                    test, type='prob')[,2])) 
    om_source_import <- merge(om_source_import,
                            data.frame(otu = names(temp_model$ranking), 
                                       rank = rank(temp_model$ranking)/
                                              max(rank(temp_model$ranking))),
                            by = 'otu', all.x = T, 
                            suffixes = c('',paste0('_', n)))
  } 
  om_loo_roc <- roc(om_loo_probs$obs~om_loo_probs$pred) 
  om_loo_otus <- merge(om_loo_otus, om_source_import,
                       by = 'otu', all.x = T, suffixes = c('',paste0('_',j)))
  om_loo_all <- rbind(om_loo_all, om_loo_probs) 
  om_loo_aucs[j] <- om_loo_roc$auc 
} 
om_loo_roc <- roc(om_loo_all$obs~om_loo_all$pred) 
om_loo_cal <- calibration_plots(om_loo_all)
